Irt plot extra

### 2022-07-06 manuscript.Rmd
adjustments in phrasing, spelling etc. in section ##analytic strategy

A quantitative cross-sectional fully anonymous, geographically unconstrained online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux]. The initial page of the online survey provided information about the survey including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised. Following this information sheet, consent was recorded digitally for the adult participants (\>18 years), whereas under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians. Filling in the entire survey was estimated to take less than 30 minutes, and participation was not compensated.
As a part of the demographic information, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in **Table 1**. Additionally, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"), to ensure high data quality and participants were asked to confirm that they participated in the survey for the first time. All questions incorporating retrospective recall were aligned to a "past four weeks" period.

We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample) totalling `r nrow(desctable.data)`.

@@

Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
Firstly, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale. Our purpose was to capture light exposure-related behaviour. In that context, the first two response options: "Does not apply/I don't know" and "Never" provided similar information. As such we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).

After the two rounds of data collection, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis. Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed. As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used polychoric correlation matrix in the EFA and employed principal axis (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020]. We used a combination of factor identification method including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018]. <!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**). -->

For reliability estimation, the "psych" package was applied [@R-psych]. Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently, to get better reliability estimates, we reported ordinal alpha for each factor obtained in the EFA [@zumbo2007ordinal]. We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.

To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI and RMSEA.

We assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`). MI evaluates whether a construct has the psychometric equivalence and the same meaning across groups [@putnick2016measurement; @klinePrinciplesPracticeStructural2015]. We used structural equation modelling framework using "lavaan" package [@R-lavaan] to assess the measurement invariance. We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$). Among MI models, the configural model is the least restrictive model and residual model is the most restrictive model. A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].

**Fourth**, as secondary analysis we identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new] using "koRpus" [@R-koRpus] package. Also, we analysed possible semantic overlap of our developed scale using ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.

**Lastly**, we developed a short form of LEBA using Item Response Theory (IRT) based analysis. We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using "mirt" package [@R-mirt]. IRT assesses the item quality by estimating item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017]. Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$). Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%. Item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017]. We discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA. We also assessed the precision of the short LEBA using Test information curve (TIC). TIC indicates the amount of information a particular scale carries along the latent trait continuum. Item fit and person fit of the fitted IRT models were also analysed to gather more evidence on validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018]. Item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit. Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].

@@

By reason of using fully anonymous online survey data, the present research project does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant. Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.

@@

After reviewing the literature, we identified several light exposure related scales. However, no scale specifically measuring the behavioural component of light exposure were found (**Supplementary Table 1**). As such, an expert panel developed a comprehensive item pool of 48 items. The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology. The 48 items were then judged based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by the expert panel. The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any. The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale.

>>>>

A quantitative cross-sectional fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux]. The initial page of the online survey provided information about the study, including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised. Subsequently, consent was recorded digitally for the adult participants (\>18 years), while under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians. Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.
As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in **Table 1**. Participants were asked to confirm that they participated in the survey for the first time. Additionally, five attention check items (e.g., "We want to make sure you are paying attention. What is 4+5?") were included among the questionnaires to ensure high data quality. All questions incorporating retrospective recall were aligned to a "past four weeks" period.

We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample), totalling `r nrow(desctable.data)`.

@@

Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale. Our purpose was to capture light exposure-related behaviour. In that context, the first two response options: "Does not apply/I don't know" and "Never" provided similar information. As such we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).

**Secondly**, the two rounds of data collection were administered. 
**Thirdly**, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using the "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis. Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed. As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020]. We applied a combination of methods including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018]. <!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**). -->

For reliability estimation, the "psych" package was applied [@R-psych]. Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently, we reported ordinal alpha for each factor obtained in the EFA [@zumbo2007ordinal] to get better reliability estimates. We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.

To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015], and SRMR does not work well with ordinal data [@RN1272]. Consequently, we judged the model fit using CFI, TLI and RMSEA.

We then assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`). MI evaluates whether a construct has the psychometric equivalence and the same meaning across groups [@putnick2016measurement; @klinePrinciplesPracticeStructural2015]. We used the structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance. We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$). Among MI models, the configural model is the least restrictive and the residual model is the most restrictive. A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].

**Fourthly**, as secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package. Also, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy of the scales.

**Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis. We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook] via the "mirt" package [@R-mirt]. IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017]. Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$). Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%. The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low = 0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017]. We discarded the items with relatively flat item information curve (information \<.2) to derive the short form of LEBA. We also assessed the precision of the short LEBA utilizing the Test information curve (TIC). TIC indicates the amount of information a particular scale carries along the latent trait continuum. Additionally, item and person fit of the fitted IRT models were  analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018]. The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, an RMSEA value $\le$.06 was considered adequate item fit. The person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness]. Here, Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].

@@

The current research project utilizes fully anonymous online survey data and therefore does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant. Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.

@@

After reviewing the literature, we identified several light exposure-related scales. However, no scale specifically measuring the behavioural component of light exposure were found (**Supplementary Table 1**). As such, an expert panel developed a comprehensive item pool of 48 items. The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology. The 48 items were then judged based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by the expert panel. The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any. The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale.
